---
title: "LasVegas"
author: "Andie"
date: "9/1/2017"
output: document
---
```{r}
#install.packages('corrplot')
#install.packages('doBy')
library(doBy) #summaryBy
library(ggplot2) # Data visualization
library(dplyr) 
library(corrplot) # correlation plot
library(plotly) # interactive map
library(rworldmap) #world map
```

Lets open our file. We notice that its a csv file and it uses semi colons to separate the values, so we will use read.csv2 to open our file and assign it to the 'df'. 
```{r}
df <- read.csv2('/Users/andiedonovan/myProjects/LasVegas/LasVegas.csv') # open file
View(df) # view the whole data set
```
We notice that some of the column names are long or messy, so lets fix that:

There are a lot of columns, so it takes a long time to rename the columns. Say we didnt really care about their length, but just wanted to remove the periods from the column names. We could use the function gsub to easily do this:
```{r}
names(df) <- gsub("\\.", "", names(df))
df
```

If we did want to go ahead and rename all of the columns, we could do that using names, colnames and a list:
```{r}
#Using names
names(df) # our current column names
names(df)[1]<-"Country" #rename just first one column
df #check that the first column name changed from 'Usercountry' to 'Country'

#Using colnames
colnames(df) # gives us the same thing
colnames(df)<-c('Country', 'NoReviews', 'NoHotelReviews', 'Helpful', 'Score', 'Stay', 'Traveler', 'Pool', 'Gym', 'Tennis', 'Spa', 'Casino', 'Internet', 'Name', 'Stars', 'NoRms', 'Continent', 'MemberYrs', 'Month', 'Weekday') #rename all of the columns using a list

df # check that it worked!
```

Theres a lot of variables in our dataset, and we probably will not need all of them for our analysis. We can create different sub datasets to allow for easier analysis of specific factors. For example, to see how whether or not a hotel has certain amenities affects its score, lets make a dataset that only includes the hotel name, country, score, and the 6 amenities listed. Lets call this new dataset amenities1:

Also notice the values for each of the variables is either 'YES' or 'NO'. Its much easier to work with numbers than characters, so lets turn each of the variables into a binary factor with 'YES'=2 and 'NO'=1

```{r}
amenities1 = df %>% 
  select(Name, Country,Score, Pool, Gym, Tennis, Spa, Casino, Internet)

amenities1$Pool<-as.numeric(amenities1$Pool)
amenities1$Gym<-as.numeric(amenities1$Gym)
amenities1$Tennis<-as.numeric(amenities1$Tennis)
amenities1$Spa<-as.numeric(amenities1$Spa)
amenities1$Casino<-as.numeric(amenities1$Casino)
amenities1$Internet<-as.numeric(amenities1$Internet)

View(amenities1)
```

Above you'll see a symbol that looks like this: %>%. This is called a pipe operator (dplyr package) and is used to insert some input or argument into a function. Its useful when we have sequences of operations and can help make the flow of the steps more readable/ easier to follow. 

Equivalently, we could nest the above code and get the same results. This would look like: amenities = select(df, c(Name, Country, Score, Pool, Gym, Tennis, Spa, Casino, Internet)). Although in this case, it doesnt make much of a difference which format you use, later on, the pipe operator is a powerful tool for applying multiple operations to one object. 

Alternative data set without hotel name & country (ie only numerical): 
```{r}
amenities2 = df %>% 
  select(Score, Pool, Gym, Tennis, Spa, Casino, Internet) # columns to be selected

amenities2 = amenities2 %>% mutate(Pool=as.factor(ifelse(Pool=="YES", "1", "0")))
amenities2 = amenities2 %>% mutate(Gym=as.factor(ifelse(Gym=="YES", "1", "0")))
amenities2 = amenities2 %>% mutate(Tennis=as.factor(ifelse(Tennis=="YES", "1", "0")))
amenities2 = amenities2 %>% mutate(Spa=as.factor(ifelse(Spa=="YES", "1", "0")))
amenities2 = amenities2 %>% mutate(Casino=as.factor(ifelse(Casino=="YES", "1", "0")))
amenities2 = amenities2 %>% mutate(Internet=as.factor(ifelse(Internet=="YES", "1", "0")))
```

Linear Regression:
Lets see how influential the 6 amenities are on the hotel's score. To do this, lets regress Pool, Gym, Tennis, Spa, Casino, and Internet on Score. We will call our linear model 'am_model'
```{r}
#am_model1<-glm(Score~Pool+Gym+Tennis+Spa+Casino+Internet, data=amenities1, family='binomial') # run regression
#summary(am_model1) # summarize linear model

#am_model2<-glm(Score~., data=amenities2, family='binomial') # run regression
#summary(am_model2) # summarize linear model

```
The first argument in the glm (generalized linear model) function is the formula. You place the independent variable on the left of the tilda and the regressors or dependent variables on the right. The second argument simply specifies that we are using our amenities data set and the third specifies that our data is binomial (ie uses logit link function). 

Look at the summary table and see if you can interpert the different columns. 
Recall: 
* Estimate (Coefficient):
* Std. Error:
* T Value:
* P(>|t|)

Correlation Matrix:
Are the variables related to each other in any way? What variables are most related to Score?
```{r}
amenities1[,3:9]
cor.amen<-cor(amenities1[,3:9], use="complete", method="pearson") 
corrplot(cor.amen)
```
 TRY:
geom_bar(stat='identity')???

Lets make a graph looking at how many hotels f
```{r}
g<- ggplot(df)+
  geom_bar(aes(x=Stars, fill = Continent), color="black") + #create bars & fill color according to continent
  theme(plot.title=element_text(hjust=0.5), # center title
        axis.text.x=element_text(angle=90, hjust=1)) + # tilt the x-axis labels 90 degrees to the left
  xlab("Hotel Stars") + # add label x axis
  ylab("Number of Hotels") + # add label y axis
  scale_x_continuous(breaks= seq(2,5,by=0.5), # make our tick marks count half stars
                     labels = c('2.0', '2.5', '3.0', '3.5','4.0', '4.5', '5.0')) + 
  ggtitle("Hotels Per Rating and Continent") #title ggplot
g #shows plot

ggplotly(g) # turn into plotly plot (interactive)
```
```{r}
avgScores<-summaryBy(Score~Country, data=mapdf, FUN=mean)
colnames(avgScores)<-c('region', 'value')
avgScores

map.world <- merge(x=map_data(map="world"),
                   y=avgScores,
                   by.x="region",
                   by.y="region",
                   all.x=TRUE)

map.world[is.na(map.world)] <- 0 # replace NAs with 0

map.world <- map.world[order(map.world$order),]

View(map.world)
#map.world <- map.world[order(map.world$order),]
#map.world

p <- ggplot(map.world) +
     geom_map(map=map.world, aes(map_id=region, x=long, y=lat, value=value)) + 
     scale_fill_gradient(low = "brown3", high = "green", guide = "colourbar")+
    coord_equal() +
         theme(axis.line=element_blank(),
               axis.text.x=element_blank(),
               axis.text.y=element_blank(),
               axis.ticks=element_blank(),
               axis.title.x=element_blank(),
               axis.title.y=element_blank(),
               panel.background=element_blank(),
               panel.border=element_blank(),
               panel.grid.major=element_blank(),
               panel.grid.minor=element_blank(),
               plot.background=element_blank(),
               legend.title=element_blank(),
               legend.position="bottom") 
p
```


```{r}
mapdf<-df %>%
    select(Country, Score)
#mapdf$Score<-as.numeric(mapdf$Score)
#mapdf %>%
#  sapply(mapdf$Score, 1,FUN=mean)

avgScores<-summaryBy(Score~Country, data=mapdf, FUN=mean)
avgScores
map.world <- map_data(map="world")
m <- ggplot() +
  theme(legend.position="none") + 
  geom_map(data=map.world, map=map.world, 
           aes(map_id=region, x=long, y=lat),
           fill="white", colour="black", size=0.25) + 
  geom_map(data=mapdf, map=map.world, aes(map_id=Country, fill=avgScores), color="white", size=0.25)
m



map.world <- merge(x=map_data(map="world"),
                   y=filtered[,c("CountryName","Value")],
                   by.x="region",
                   by.y="CountryName",
                   all.x=TRUE)
#map.world <- map.world[order(map.world$order),]



avgScores = as.data.frame(avgScores)
m<-ggplot(avgScores, aes(map_id = Country)) + 
    geom_map(aes(fill = Score.mean), map = worldMap, size=0.3) + 
    expand_limits(x = worldMap$long, y = worldMap$lat) 
m

```

